---
title: "fact-check"
format: html
editor: visual
---

# To run this code, run the init Quarto document first.

"A Baltimore Banner data analysis found majority-Black and majority-minority neighborhoods do have a slight disadvantage in access to pharmacies."

```{r}

blocks_by_neighborhood %>%
  group_by(x2020_majority_neighborhood_type) %>%
  summarise(average_min_distance = mean(min_distance_to_pharmacy),
            median_min_distance = median(min_distance_to_pharmacy),
            max_min_distance = max(min_distance_to_pharmacy))

```

"The average distance of all city blocks in Baltimore to a pharmacy is about three-tenths of a mile."

```{r}

#calculating tenths of a mile
mean(blocks_by_neighborhood$min_distance_to_pharmacy)/1609

```

"Blocks in majority-Black and majority-minority neighborhoods were just above average, and majority-white and majority-Hispanic neighborhoods were just below."

```{r}

blocks_by_neighborhood %>%
  group_by(x2020_majority_neighborhood_type) %>%
  summarise(average_min_distance = mean(min_distance_to_pharmacy),
            median_min_distance = median(min_distance_to_pharmacy),
            max_min_distance = max(min_distance_to_pharmacy))

```

"A slightly higher share of majority Black neighborhoods don't have a pharmacy."

```{r}

neighborhoods_by_pharmacies %>%
  st_drop_geometry() %>%
  mutate(has_pharmacy = case_when(
    pharmacies > 0 ~ TRUE,
    TRUE ~ FALSE
  )) %>%
  group_by(x2020_majority_neighborhood_type, has_pharmacy) %>%
  count() %>%
  pivot_wider(values_from = n, names_from = has_pharmacy) %>%
  clean_names() %>%
  mutate(perc_without = false/(false+true))

```
